
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# echarts4r.assets

Assets for the [echarts4r](https://echarts4r.john-coene.com) package.

## Install

`echarts4r` is available from CRAN, `echarts4r.assets` is available from [Github](https://github.com/JohnCoene/echarts4r) only:

```r
install.packages("echarts4r")

# install.packages("devtools")
remotes::install_github("JohnCoene/echarts4r.assets")
```

## Note

This is a large package due to the size of the high fidelity textures it contains (currently holding 11.6Mb of assets), it might take a small minute to install. However, this does not mean that it crowds tyour envrionment, on the contrary it includes but a few functions.

## Assets

The following assets are available.

```{r}
echarts4r.assets::ea_bank()
```

## Example

```{r}
library(echarts4r)
library(echarts4r.assets)

e_charts() %>% # initialise
  e_rm_axis("x") %>% # remove axis
  e_rm_axis("y") %>% 
  e_globe(
    environment = ea_asset("starfield"),
    base.texture = ea_asset("world")
  ) 
```

*Though the pacakge is designed with `echarts4r` in mind, the assets can technically be used for other packages*
