---
title: "Examples"
author: "John Coene"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

All assets currently available.

```{r}
library(echarts4r)
library(echarts4r.assets)
```

For demonstration purposes let's create a basic, non working plot to which we'll add assets.

```{r} 
base <- e_charts() %>% # initialise
  e_rm_axis("x") %>% # remove axis
  e_rm_axis("y") 
```

## Examples

*These are not all the textures included*

```{r}
base %>% 
  e_globe(
    environment = ea_asset("starfield"),
    base.texture = ea_asset("world")
  )
```

```{r}
base %>% 
  e_globe(
    environment = ea_asset("galaxy"),
    base.texture = ea_asset("jupiter")
  )
```

```{r}
base %>% 
  e_globe(
    environment = ea_asset("starfield"),
    base.texture = ea_asset("world topo"),
    height.texture = ea_asset("elevation 4k")
  )
```

```{r}
base %>% 
  e_globe(
    environment = ea_asset("starfield"),
    base.texture = ea_asset("world topo"),
    height.texture = ea_asset("elevation 4k"),
    displacementScale = 0.1
  )
```

```{r}
base %>% 
  e_globe(
    environment = ea_asset("starfield"),
    base.texture = ea_asset("world"),
    layers = list(
      list(
        type = "overlay",
        shading = "lambert",
        texture = ea_asset("clouds trans"),
        distance = 5
      )
    )
  )
```

```{r}
base %>% 
  e_globe(
    displacementScale = 0.1,
    baseColor = "#000",
    shading = "hatching",
    height.texture = ea_asset("elevation 4k"),
    hatchingMaterial = list(
      hatchingTextures = list(
        ea_asset("hatch0"),
        ea_asset("hatch1"),
        ea_asset("hatch2"),
        ea_asset("hatch3"),
        ea_asset("hatch4"),
        ea_asset("hatch5")
      ),
      textureTiling = list(10, 10)
    ),
    postEffect = list(
      enable = TRUE,
      edge = list(
        enable = TRUE
      )
    )
  )
```

## Custom assets

You can use your own assets too of course. In shiny simply place them in your `www` directory and reference the file name as texture, see the shiny section for more information. In R markdown you can simply use `ea_convert` to convert your texture.

